Deep Probabilistic Models for Camera Geo-Calibration

### 2018-09-18 chapters/discussion/discussion.tex
last editing

The goal of geo-calibration is to learn the camera pose, location and
the time when the image was captured.
Our thesis focused on developing deep geo-calibration algorithms for
image understanding.
Compared to previous work, our approaches output probabilistic
predictions that are able to handle the uncertainty of the scene
better. Furthermore, we also show that
learning to geo-calibrate a camera allows us to implicitly learn to
understand the content of the scene.

In \chapref{mcmc}, we proposed a flexible model to compute the
probability over all geo-calibration parameters. In the high
dimensional space of geo-calibration parameters, we defined a score
function for every point, to measure how well the
geo-calibration parameters match the content of the input image.
The score function is a weighted summation of a series of
constraint functions. It is proportional to the probability density
function of the distribution. Since the analytic solution to the
integral of the score function does not exist, we approximated the
probability density function using MCMC method. Our model is flexible
to any constraint function for geo-calibration parameters. We also
demonstrated in our experiment that more accurate predictions can be
obtained if the score function consists of more constraints.

In \chapref{fasthorizon}, we focused on developing constraint function
for the camera pose. Assuming the focal length is known, the camera
roll and pitch angle can be derived from the horizon line position.
Our algorithm identifies the horizon line from the input image
satisfying the Manhattan world assumption. Compared to the previous
work, which applies a bottom-up approach where the horizon line is
estimated after the vanishing point identification, we proposed a
novel horizon-first approach where finding horizon line candidates is
prior to identifying vanishing points.  As the first step, we trained
a CNN to estimate the probability distribution over the horizon line.
Then we sample horizon line candidates from the distribution. For each
horizon candidate, we detect likely vanishing points on it. Compared
to previous work which searches for vanishing points on the 2D image
frame, our method is able to accelerate the searching process by
reducing the searching space to 1D. The probability of the horizon
line is measured by how convincing are the vanishing points found on
it.

In \chapref{whenwhere}, we developed the constraint function for 
the image capture time and the camera location. 
We trained a CNN on a large dataset to learn to predict the discrete
probabilities over location and time given the input image.
Unlike full supervision methods which require tedious work for manual
annotations, our training dataset consists of millions webcam
frames and smart phone photos with free time/location tags.
In the experiments, we demonstrated that geo-calibrating the camera
also helps learn useful image representations for image understanding.

In \chapref{crosstransf}, we exploited overhead imagery to construct
the constraint function for the camera orientation and location.
We trained a CNN that can estimate the semantic layout of the ground
view image from the overhead image. During training, the CNN learns the
pixel-to-pixel correspondences from the aerial image to the ground
image. 
It then projects the semantic layout the of the overhead image to the
ground view according to the learned correspondence.
When computing the output of the constraint function, we feed the
aerial image of given location and orientation to the network. By
comparing the aerial-to-ground layout with the layout computed from
the ground image, we measure the consistency between these two and use
consistency value as the output of the constraint function. 
In our experiments, we also demonstrated the efficiency of our method
for pre-training CNNs for aerial image segmentation.

This thesis proposed a flexible probabilistic framework for image
geo-calibration. The key to the success of the framework is to find
constraint functions that can accurately model the relationship between
geo-calibration parameters and the image content. 
We developed constraint functions for different set of parameters to
fit to the framework. 
Furthermore, we also show that learning to geo-calibrate cameras helps
learning useful features for image understanding. There are several
possible future research directions for extending this work,
including: exploiting map data in cross-view learning, replacing the
CNN networks in our algorithms with Bayesian neural networks (BNNs).
Overall, we hope our work can provide new ways for geo-calibration and
pretext task for learning image representations.

>>>>

The goal of geo-calibration is to learn the camera pose, location and
the time when the image was captured.
Our thesis focused on developing deep geo-calibration algorithms for
image understanding.
Compared to previous work, our approaches output probabilistic
predictions that handle the uncertainty of the scene
better. Furthermore, we show that
learning to geo-calibrate a camera allows us to implicitly learn to
understand the content of the scene.

In \chapref{mcmc}, we proposed a flexible model to compute the
probability over geo-calibration parameters. We defined a score
function in the space of geo-calibration parameters, to measure how
well the geo-calibration parameters are able to describe the content
of the input image.
The score function is the summation of a series of weighted
constraint functions. It is proportional to the probability density
function (PDF) of the distribution over the geo-calibration parameter setting.
Since the analytic solution to the
integral of the score function does not exist, we approximated the
PDF using MCMC method. Our model is flexible such that one can apply
any kind and number of constraint functions for geo-calibration
parameters. We also demonstrated in our experiment that 
score function with more constraint functions yields more accurate
predictions.

In \chapref{fasthorizon}, we developed a constraint function for the
camera pose. Since the camera roll and pitch angle can be derived from
the horizon line position, our algorithm focuses on identifying the
horizon line from the input image.
Compared to the previous work, which applies bottom-up
approaches where the horizon line is estimated after finding vanishing
points, we proposed a novel horizon-first approach where
identifying possible horizon lines is prior to detecting vanishing
points. 
Firstly, we trained a CNN to estimate the probability distribution
over the horizon line. Then we sample horizon line candidates from
it. For each horizon candidate, we detect likely
vanishing points on it. Unlike the previous work which searches for
vanishing points on the 2D image frame, our method is able to
accelerate this process by reducing the searching space to
1D (a line). The probability of the horizon line is measured by how
convincing are the vanishing points found on it.

In \chapref{whenwhere}, we developed the constraint function for 
the image capture time and the camera location. 
We trained a CNN on a large dataset to predict the discrete
probabilities over the capture time and the camera location given the
input image.
Unlike full supervision methods which require tedious work for manual
annotations, our training dataset consists of millions of webcam
frames and smart phone photos with free time/location tags.
In the experiments, we demonstrated that learning to geo-calibrate the
camera helps learn useful image representations for image understanding.

In \chapref{crosstransf}, we exploited overhead imagery to construct
the constraint function for the camera orientation and location.
We trained a CNN to estimate the semantic layout of the
ground-view image from the overhead image. During training, the CNN
learns the pixel-to-pixel correspondences from the aerial image to the
ground image. Then it projects the semantic layout the of the overhead
image to the ground view according to the learned correspondences.
When computing the output of the constraint function, we feed the
aerial image of given location and orientation to the network. By
comparing the aerial-to-ground layout with the layout computed from
the ground image, we measure the consistency between these two and use
the consistency value as the output of the constraint function. 
In our experiments, we also demonstrated the efficiency of our method
for pre-training CNNs for aerial image segmentation.

This thesis proposed a flexible probabilistic framework for image
geo-calibration. The key to the success of this framework is to find
constraint functions that can accurately model the relationship between
geo-calibration parameters and the content of the image. 
We developed constraint functions for different set of parameters to
fit to the framework. 
Furthermore, we also showed that learning to geo-calibrate cameras helps
learning useful features for image understanding. There are several
possible future research directions for extending this work,
including: exploiting map data in cross-view learning, replacing the
CNN networks in our algorithms with Bayesian neural networks (BNNs).
Overall, we hope our work can provide new ways for geo-calibration and
image feature learning.
